\section{Introduction}
\label{sec:intro}

\subsubsection{BOINC}

BOINC is a system for distributing the workload of scientific simulations. Users of BOINC have a client running that solves work units (WU) for the specific projects. A work unit consists of code and specific parameters for which the code is run.  After the work unit is completed the BOINC client sends back the results to the BOINC servers, where the results are analyzed.

TODO: update project list
One example for a BOINC project is the World Community Grid [WCG], which consists of various other projects, for example to solve cancer [Cancer] or beat Ebola [Ebola] . SETI@home [SETI], which looks for signs of alien life by monitoring electromagnetic radiation from space for patterns, is another well-known project.  In total there are about 40 BOINC projects, but only the BOINC projects on the [Whitelist] help users earn Gridcoins.

The information which researcher has computed how many work units is stored on the BOINC server. The unit of work done is a credit (cobblestone), which is 1,000 double-precision MFLOPS based on the Whetstone benchmark [Whetstone].  The RAC is the average amount of credits earned  per day.

A CPID (Cross Project Identifier) is a number that links together the participation of a single user in all the different projects with a single common identifier, with a CPID one can see the research done by one user over all different projects this user participates in.

There are also teams in BOINC, users can join teams and the work done by each member of the team is added to get the work done by the team. It is necessary for a Gridcoin-researcher to be a part of team ?Gridcoin?, which on some projects is listed as ?gridcoin?, lowercase.

\subsubsection{Gridcoin}

TODO: 

\subsection{Setting it up}

For setting up BOINC and the Gridcoin client to earn Gridcoins by running scientific simulations on your computer follow the tutorial on gridcoin.us
The steps involved are:
* Install BOINC
* Install and configure Gridcoin wallet 
* Acquire Gridcoin and move them to your wallet
* Send beacon
